---
title: "analyze_graphical_conventions_data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
library(brms)
library(broom.mixed)
library(tidyboot)
library(here)
```

# Import group data

To center every condition at the same starting point, we generate a "baseline" data-frame that computes BIS for the "pre-" phase, grouping by condition and gameID. Then we add this "baseline" bis to each row of original bis dataframe.

```{r}
version = '1.2' # 2.0 / 1.2
data_prefix = here(paste0('data/experiment/refgame', version, '/graphical_conventions'))
path = ifelse(version == '1.2', 'run3run4.csv', 'run5_submitButton.csv')

d <- paste0(data_prefix, '_group_data_', path) %>%
  read_csv() %>% 
  select(-png)


d.bis.drawDuration.raw <- paste0(data_prefix, '_bis_drawDuration_', path) %>%
  read_csv() %>% 
  select(-`...1`)

d.bis.drawDuration <- d.bis.drawDuration.raw %>%
  filter(repetition==0) %>%
  group_by(condition,gameID) %>%
  summarize(bis_baseline = mean(bis)) %>%
  inner_join(d.bis.drawDuration.raw, 
             by = c('condition','gameID'), 
             suffix = c("","_baseline")) %>%
  ungroup() %>%
  mutate(repetition = ifelse(condition == 'control' & repetition == 1, 7, repetition),
         bis_relative = bis - bis_baseline,
         repetition_1 = repetition + 1)
```
Some basic statistics about the dataset to report

```{r}
numGames <- d.bis.drawDuration %>% 
  pull(gameID) %>%
  unique() %>%
  length()

cat("we collected", numGames, "games")
```


# Behavioral Results

## Section 2.1: Participants learn to communicate more effectively

### Make Fig. 3A

We want 95% CIs to be computed over participant means, so we bootstrap re-sample at the level of participants

```{r}
d.bis.drawDuration %>% 
  group_by(gameID, condition, repetition_1) %>%
  summarize(bis_relative = mean(bis_relative)) %>%
  group_by(condition, repetition_1) %>% 
  tidyboot_mean(bis_relative, nboot=1000) %>%
  ggplot(aes(x=repetition_1, y=empirical_stat, color=condition, fill=condition)) + 
    geom_line(size=1.5)+
    geom_ribbon(aes(ymin=ci_lower, ymax = ci_upper), alpha=.25, color=NA,
                data = . %>% filter(condition == 'repeated')) + 
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                  data = . %>% filter(condition == 'control')) + 
    labs(y = "relative efficiency", x = "repetition") +
    scale_y_continuous(breaks = seq(-0.5,2.5,0.5)) +
    scale_color_manual(values=c("#808080", "#163c4e")) + 
    scale_fill_manual(values=c("#808080", "#163c4e")) + 
    theme_few() +
    theme(legend.position = c(0.8, 0.2), 
          text = element_text(size=18), 
          element_line(size=1), 
          element_rect(size=2, color="#00000"))

tmp_prefix = here('../graphical_conventions_latex/natcomms2020/figures/')
ggsave(paste0(tmp_prefix, 'fig3a_refgame_BIS', version, '.pdf'), width=14, height = 10, units='cm')
```

### Simple effect of BIS in repetition condition

```{r}
lmer(bis ~ poly(repetition, 2) + (0 + poly(repetition, 1) | gameID),
      data = d.bis.drawDuration %>% filter(condition == 'repeated'),
      control = lmerControl(optimizer = 'bobyqa')) %>%
  summary()

glmer(outcome ~ poly(repetition, 2) + (1 + poly(repetition,1) | gameID),
      data = d %>% filter(condition == 'repeated'),
      family='binomial',
      control=glmerControl(optimizer = 'bobyqa')) %>%
  summary()

lmer(drawDuration ~ poly(repetition, 2) + (1 + poly(repetition,1) | gameID),
     data = d %>% filter(condition == 'repeated'),
     control=lmerControl(optimizer = 'bobyqa')) %>%
  summary()

lmer(numStrokes ~ poly(repetition,2) + (1 + poly(repetition,1) | gameID), 
     data = d %>% filter(condition=='repeated'),
     control=lmerControl(optimizer = 'bobyqa')) %>%
  summary()
```

### Bayesian versions of these (2.1A)

```{r}
# using mo() for monotonic predictors
bis.brm <- brm(bis ~ mo(repetition) + (0 + mo(repetition) | gameID),
               data = d.bis.drawDuration %>% filter(condition == 'repeated'))

acc.brm <- brm(outcome ~ mo(repetition) + (1 + mo(repetition) | gameID),
              data = d %>% filter(condition == 'repeated'),
              family='bernoulli')

rt.brm <- brm(drawDuration ~ mo(repetition) + (1 + mo(repetition) | gameID),
              data = d %>% filter(condition == 'repeated'))

strokes.brm <- brm(numStrokes ~ mo(repetition) + (1 + mo(repetition) | gameID), 
                   data = d %>% filter(condition=='repeated'))

```

### Figure 4A 

(number of strokes over time in repeated condition)

```{r}
d %>%
  filter(condition == 'repeated') %>%
  mutate(repetition = repetition + 1) %>%
  group_by(repetition) %>%
  tidyboot_mean(numStrokes) %>%
  ggplot(aes(x = repetition, y = empirical_stat)) +
    geom_point(colour = '#163c4e',size = 2) +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F, color = '#163c4e') +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0, color = '#163c4e') +
    theme_few() +
    scale_x_continuous(labels = c(1,2,3,4,5,6,7,8), breaks = c(1,2,3,4,5,6,7,8)) +
    ylab('number of strokes') +
    theme(legend.position = c(0.5, 0.8), text = element_text(size=18), 
          element_line(size=1), element_rect(size=2, color="#00000"),
          aspect.ratio = 2) 
  

ggsave(paste0(tmp_prefix, 'fig4a_strokes', version, '.pdf'), height = 10, width = 7, units = 'cm', useDingbats = F)
```

## Section 2.2: Object-specificity

### Check accuracies

No differences between condition in pre phase.

```{r}
d %>%
  filter(repetition == 0 | repetition == 7) %>% 
  mutate(phase = as.factor(ifelse(repetition == 0, 'pre', 'post')),
        condition = as.factor(condition)) %>%
  group_by(gameID, condition, phase) %>%
  summarize(acc = mean(outcome), rt = mean(drawDuration)) %>%
  pivot_wider(names_from = condition, values_from = c(acc, rt)) %>%
  mutate(diff_rt = rt_control - rt_repeated,
         diff_acc = acc_control - acc_repeated) %>%
  #gather(metric, value, rt_post, rt_pre, acc_post, acc_pre, diff_rt, diff_acc) %>%
  gather(metric, value, rt_control, rt_repeated, acc_control, acc_repeated, diff_rt, diff_acc) %>%
  group_by(metric, phase) %>%
  tidyboot_mean(value)
```

Check 1st vs. 2nd occurrence for repeated vs. control

```{r}
d %>%
  filter(repetition == 0 |
           (condition == 'repeated' & repetition == 1) |
           (condition == 'control' & repetition == 7)) %>% 
  left_join(d.bis.drawDuration, by = c('gameID', 'trialNum', 'repetition', 'condition')) %>%
  mutate(occurrence = as.factor(ifelse(repetition == 0, 'first', 'second')),
        condition = as.factor(condition)) %>%
  group_by(condition, occurrence) %>%
  summarize(acc = mean(outcome.x), rt = mean(drawDuration.x), bis = mean(bis_relative)) 

```

### 'Design plot' for analysis (Fig. 3B)

```{r}
d.means <- d.bis.drawDuration %>%
  ungroup() %>%
  filter(repetition == 7) %>% 
  mutate(condition = as.factor(condition)) %>%
  group_by(gameID, condition) %>%
  summarize(bis = mean(bis_relative))

d.means %>%
  ggplot(aes(x = condition, y = bis, color = condition, fill = condition, group = gameID)) +
    geom_point(position = position_jitter(width = 0.1, seed = 123), alpha = 0.1, shape=21,) +
    geom_line(position = position_jitter(width = 0.1, seed = 123), 
              alpha = 0.05, color = 'black') +
    geom_line(aes(group = 1), size = 1, alpha = 0.5, color = 'black', 
              data = d.means %>% group_by(condition) %>% summarize(bis = mean(bis))) +
    geom_point(aes(group = NA), size = 5, data = d.means %>% group_by(condition) %>% summarize(bis = mean(bis))) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper, y = empirical_stat, group = NA), 
                  data = d.means %>% group_by(condition) %>% tidyboot_mean(bis),
                  width =0, size = 2) +
    geom_hline(yintercept = 0) +
    theme_few() +
    labs(x = '') +
    theme(aspect.ratio = 2, legend.position = 'none')

ggsave(paste0(tmp_prefix, 'fig3b_variability', version, '.pdf'), units = 'cm', height = 9, width = 5)
```

### Model

Now we run a mixed-effects model to evaluate an interaction in BIS changes across conditions. The maximal model for the interaction between repetition and condition is this:

```
interaction_lmm <- lmer(bis ~ phase * condition + (0 + phase*condition | gameID)
```

```{r}
d.bis.drawDuration %>%
  ungroup() %>%
  filter(repetition == 0 | repetition == 7) %>% 
  mutate(phase = as.factor(ifelse(repetition == 0, 'pre', 'post')),
         condition = as.factor(condition)) %>%
  lmer(bis ~ phase * condition + (0 + phase * condition | gameID) ,
        data = .,
       control = lmerControl(optimizer = 'bobyqa'),
        contrasts = list(phase = contr.sum(2), condition = contr.sum(2))) %>%
  summary()
```

Double-check normalizing just within pre-post (footnote)

```{r}
d.bis.drawDuration.prepost.raw <- paste0(data_prefix, '_bis_prepostonly_drawDuration_', path) %>%
  read_csv() %>% 
  select(-`...1`)

d.bis.drawDuration.prepost.raw %>%
  filter(repetition == 0 | repetition == 7) %>% 
  mutate(phase = as.factor(ifelse(repetition == 0, 'pre', 'post')),
         condition = as.factor(condition)) %>%
  lmer(bis ~ phase * condition + (0 + phase * condition | gameID) ,
        data = .,
       control = lmerControl(optimizer = 'bobyqa'),
        contrasts = list(phase = contr.sum(2), condition = contr.sum(2))) %>%
  summary()
```

### Bayesian version

```{r}
cont.brm.input <- d.bis.drawDuration %>% 
  ungroup() %>%
  filter(repetition == 0 | repetition == 7) %>% 
  mutate(phase = as.factor(ifelse(repetition == 0, 'pre', 'post')),
         condition = as.factor(condition))

contrasts(cont.brm.input$condition) <- "contr.sum"
contrasts(cont.brm.input$phase) <- "contr.sum"

cont.brm <-  brm(bis ~ phase * condition + (0 + phase * condition | gameID),
                 data = cont.brm.input)
```

### Double-check the mixed-effects model just on raw accuracy and raw RT.

```{r}
model.input <- d %>%
  filter(phase %in% c('pre', 'post')) %>% 
  mutate(phase = as.factor(phase),
         condition = as.factor(condition),
         outcome = as.numeric(outcome)) 

contrasts(model.input$condition) <- "contr.sum"
contrasts(model.input$phase) <- "contr.sum"

glmer(outcome ~ phase * condition + (1 + phase * condition | gameID), 
                family= 'binomial', data = model.input,
                control = glmerControl(optimizer = 'bobyqa')) %>%
  summary()

lmer(drawDuration ~ phase * condition + (1 + phase * condition | gameID), 
      data = model.input,
      control = lmerControl(optimizer = 'bobyqa')) %>%
  summary()

### Bayesian version
acc.control.brm <- model.input %>%
  brm(outcome ~ phase * condition + (1 + phase * condition | gameID), 
      family= bernoulli(), 
      data = . )

rt.control.brm <- model.input %>%
  brm(drawDuration ~ phase * condition + (1 + phase * condition | gameID), 
      data = . )
```

### Sketch features (Fig. 4B)

To measure within-interaction convergence on sketch features, first import pre-processed matrices generated in ipynb...

```{r}
library(reticulate)
featureprefix <- paste0('../data/features/refgame', version)
np <- import("numpy")
F_mat_raw_nonorm = np$load(paste0(featureprefix, '/FEATURES_vgg_FC6.npy'))
```

```{r}
source('helpers/helpers.R')
library(broom)
detach('package:lmerTest')
M_mat = read_csv(paste0(featureprefix, '/METADATA.csv')) %>%
  mutate(path = gsub('/home/jefan/graphical_conventions/results/sketches/refgame.*/png/', '', path)) %>%
  mutate(path = gsub('.png', '', path)) %>%
  separate(path, into = c('gameID', 'category', 'target', 'repetition'), sep = '_') %>%
  group_by(gameID, target) %>%
  mutate(condition = ifelse(length(repetition) == 2, 'control', 'repeated')) %>%
  filter(condition == 'repeated') %>%
  select(gameID, target, repetition, feature_ind) %>%
  mutate(feature_ind = feature_ind + 1,
         repetition = as.numeric(repetition)) %>% # Have to correct for R 1-indexing...
  arrange(gameID, target, repetition) 
```

run stats

```{r}
library(lmerTest)
true_lmer.within <- make_within_df(M_mat, F_mat_raw_nonorm, 'cor') %>% 
  filter(rep2 == rep1 + 1) %>% 
  ungroup()

lmer(sim ~ poly(rep1, 2) + (1 + poly(rep1, 1)  || gameID) +  (1 + poly(rep1, 1)  || target), 
     data = true_lmer.within) %>%
  summary()

stability.brm <- brm(sim ~ mo(rep1) + (1  | gameID), 
                     data = true_lmer.within) 
print(summary(stability.brm), digits = 10)
```

compute both true empirical & permuted output

```{r}
# num_permutations <- 1000
# empirical.within <- compute_within_convergence(
#   M_mat, F_mat_raw_nonorm, 'empirical', method = 'cor', nboot = 1000
# )
```

Make Fig. 4B

```{r}
true_lmer.within %>%
  group_by(rep1, gameID) %>%
  summarize(sim = mean(sim)) %>%
  group_by(rep1) %>%
  tidyboot_mean(sim) %>%
  ggplot(aes(x = rep1, y = empirical_stat)) +
    geom_point(size = 2) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F) +
    scale_color_manual(values=c("#d07e93", "#163c4e")) + 
    scale_fill_manual(values=c("#d07e93", "#163c4e")) + 
    scale_x_discrete(labels = c('(1,2)','(2,3)', '(3,4)', '(4,5)', '(5,6)' ,'(6,7)','(7,8)')) +
    ylim(.5, .8) +
    ylab('correlation') +
    ggtitle('within-pair') +
    theme_few() +
    xlab('repetition pair') +
    guides(color = F, fill = F) +
    theme(legend.position = c(0.5, 0.8), text = element_text(size=18), 
          element_line(size=1), element_rect(size=2, color="#00000"),
          aspect.ratio = 2)

ggsave(paste0(tmp_prefix, 'fig4b_stability', version, '.pdf'), height = 10, width = 7, units = 'cm', useDingbats = F)
```

## Section 2.3: Conventions are interaction-specific 

### load in data from control conditions

```{r}
d.recog <- read_csv(paste0(data_prefix, '_recog_data_bis_', path)) %>%
  mutate(version = factor(version, levels = c("refgame","yoked","scrambled40"), 
                          labels = c("communication", "yoked", "shuffled" )))  %>%
  filter(!is.na(version))
```

get counts for each condition

```{r}
d.recog %>%
  group_by(gameID, version) %>%
  tally() %>%
  group_by(version) %>%
  tally()
```

### Make Fig. 5A

(plotting BIS  from refgame, yoked, and scrambled40 experiments)

```{r}
d.recog %>%
  group_by(gameID, version,repetition_1) %>%
  summarize(bis_relative = mean(bis_relative)) %>%
  group_by(version, repetition_1) %>%
  tidyboot_mean(bis_relative) %>%
  ggplot(aes(x = repetition_1, y = empirical_stat, color = version, fill = version)) +
    geom_line(size=1.5) +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.2, color = NA) +
    theme_few() +
    ylab('relative efficiency') +
    xlab('repetition') +
    scale_x_continuous(breaks=seq(1,8,by=1)) + 
    scale_color_manual(values=c("#163c4e", "#658da0", '#54792f')) + 
    scale_fill_manual(values=c("#163c4e", "#658da0", '#54792f')) +   
    theme(legend.position = c(0.18, 0.8), text = element_text(size=18), element_line(size=1), element_rect(size=2, color="#00000")) +
    theme(legend.text=element_text(size=12), legend.background = element_rect(fill="transparent"))

ggsave(paste0(tmp_prefix, 'fig5a_recog', version, '.pdf'), width=14, height = 10, units='cm')
```
### Make Fig. 5B

```{r}
d.means <- d.recog %>%
  ungroup() %>%
  filter(repetition == 7) %>% 
  mutate(version = as.factor(version)) %>%
  group_by(orig_gameID, version) %>%
  summarize(bis = mean(bis_relative))

d.means %>%
  ggplot(aes(x = version, y = bis, color = version, fill = version, group = orig_gameID)) +
    geom_point(position = position_jitter(width = 0.1, seed = 123), alpha = 0.1, shape=21,) +
    geom_line(position = position_jitter(width = 0.1, seed = 123), 
              alpha = 0.05, color = 'black') +
    geom_line(aes(group = 1), size = 1, alpha = 0.5, color = 'black', 
              data = d.means %>% group_by(version) %>% summarize(bis = mean(bis))) +
    geom_point(aes(group = NA), size = 5, data = d.means %>% group_by(version) %>% summarize(bis = mean(bis))) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper, y = empirical_stat, group = NA), 
                  data = d.means %>% group_by(version) %>% tidyboot_mean(bis),
                  width =0, size = 2) +
    geom_hline(yintercept = 0) +
    theme_few() +
    labs(x = '') +
    theme(aspect.ratio = 2, legend.position = 'none')

ggsave(here('../graphical_conventions_latex/natcomms2020/figures/fig5b_variability.pdf'), units = 'cm', height = 10, width = 5)
```

### Yoked vs. scrambled40 analysis

```{r}
d.recog %>% 
  filter(version %in% c('yoked', 'shuffled')) %>%
  lmer(bis_relative ~ version * poly(repetition, 2) + (1 + version * poly(repetition, 1) || orig_gameID), 
       control = lmerControl(optimize = 'bobyqa'),
              data = .) %>%
  summary()

recog.brm <- d.recog %>% 
  filter(version %in% c('yoked', 'shuffled')) %>%
  brm(bis_relative ~ version * mo(repetition) + (1 + version * mo(repetition) || orig_gameID), 
       data = .) 
```

### Yoked vs. communication analysis

```{r}
d.recog %>% 
  filter(version %in% c('communication', 'yoked')) %>%
  lmer(bis_relative ~ version * poly(repetition, 2) + (1 + poly(repetition, 1)  || orig_gameID),
       data = .) %>%
  summary()
```

Comparing raw accuracy and RT

```{r}
d.acc %>% 
  filter(version %in% c('communication','yoked')) %>%
  filter(condition == 'repeated') %>%
  lmer(accuracy ~ version + (1 | gameID),
      data = .) %>%
  summary()
```

### Analysis of change in raw accuracy & RT across all three groups: communication, yoked, shuffled

```{r}
d.acc <- read_csv(paste0(data_prefix, '_recog_data_', path)) %>%
  mutate(version = factor(version, levels = c("refgame","yoked","scrambled40"), 
                          labels = c("communication", "yoked", "shuffled" ))) %>%
  mutate(repetition = ifelse(version == 'communication' & condition == 'control' & repetition == 1, 7, repetition)) %>%
  group_by(version,condition, gameID,repetition) %>%
  summarize(accuracy=mean(correct), RT = mean(logRT)) %>%
  filter(!is.na(version))

d.acc %>%
  gather(measure, value, accuracy, RT) %>%
  filter(repetition %in% c(0,7)) %>%
  group_by(measure, condition, repetition, version) %>%
  summarize(m=mean(value)) %>%
  spread(repetition, m) %>%
  mutate(diff = `7` - `0`) 
```

Plotting accuracy timecourse for communication and yoked (SXXX)

```{r}
d.acc.rt.boot = d.acc %>%
  gather(measure, value, accuracy, RT) %>%
  group_by(measure, version,condition,repetition) %>%
  tidyboot_mean(value) %>%
  ungroup()

d.acc.rt.boot %>%  
  ggplot(aes(x = repetition, y = empirical_stat, 
             color = version, fill = version, linetype = condition)) +
    geom_line() +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.2, color = NA) +
    theme_few() +
    ylab('') +
    xlab('repetition') +
    facet_grid(measure ~ version, scales = 'free') +
    scale_x_continuous(breaks=seq(1,8,by=1)) + 
    scale_color_manual(values=c("#163c4e", "#d07e93", '#54792f')) + 
    scale_fill_manual(values=c("#163c4e", "#d07e93", '#54792f')) +   
    scale_linetype_manual(values = c('dotted', 'solid')) +
    theme(legend.position = 'top', 
          element_line(size=1), element_rect(size=2, color="#00000"),
          text = element_text(size=12),
          legend.text=element_text(size=10), 
          legend.background = element_rect(fill="transparent"),
          aspect.ratio = 1) +
    guides(color = 'none', fill = 'none') 
    #ylim(0.6, 1) +

tmpprefix = here('../graphical_conventions_latex/natcomms2020/figures/rt-and-acc-recog')
ggsave(paste0(tmpprefix, version, '.pdf'), height = 4, width = 4, units = 'in', useDingbats = F)
```

### Interaction history contributes to gains in recognition performance (Fig. 4C)

Compute between-interaction divergence 

```{r}
gamepair.df <- M_mat %>%
  group_by(target, repetition) %>%
  do(flatten_sim_matrix(get_sim_matrix(., F_mat_raw_nonorm, method = 'cor'),
                        .$gameID)) %>%
  unite(col = 'gamepair', dim1, dim2)

true_lmer.across <- lmer(sim ~ poly(repetition, 2) + (1 + repetition | gamepair) + (1 + repetition | target), 
                         data = gamepair.df,
                         control = lmerControl(optimizer = 'bobyqa'))
summary(true_lmer.across)
```

```{r}
empirical.across <- compute_across_similarity(M_mat, F_mat_raw_nonorm,   
                                              'raw_cor_nonorm', method = 'cor', nboot = 1000)
```

```{r}
ggplot(d.toplot, aes(x = repetition, y = empirical_stat, group = sample_id, 
                     color = sample_id, fill=sample_id)) +
  geom_ribbon(alpha = 0.25, aes(ymin = ci_lower, ymax = ci_upper), color = NA,
              data = d.toplot %>% filter(sample_id == 'baseline')) + 
  geom_line(size = 1, linetype = 'dashed', data = d.toplot %>% filter(sample_id == 'baseline')) +
  geom_point(size = 2, alpha = 1, data = d.toplot %>% filter(sample_id == 'raw_cor_nonorm')) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0,
                 data = d.toplot %>% filter(sample_id == 'raw_cor_nonorm')) +
  geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F,
              data = d.toplot %>% filter(sample_id == 'raw_cor_nonorm')) +
  scale_color_manual(values=c("#d07e93", "#163c4e")) + 
  scale_fill_manual(values=c("#d07e93", "#163c4e")) + 
  xlim(0.5, 8.5) +
  scale_x_continuous(labels = c(1,2,3,4,5,6,7,8), breaks = c(1, 2,3,4,5,6,7,8)) +
  ylim(.5, .8) +
  ylab('correlation') +
  ggtitle('between-pair') +
  theme_few() +
  guides(color = F, fill = F) +
  theme(legend.position = c(0.5, 0.8), text = element_text(size=18), 
        element_line(size=1), element_rect(size=2, color="#00000"))

tmpprefix = paste0('plots/refgame',version, '/across')
ggsave(paste0(tmpprefix, version, '.pdf'), height = 10, width = 7, units = 'cm', useDingbats = F)
```

## Section 2.4: Diagnosticity

```{r}
d.diagnosticity <- read_csv(here('data/diagnosticity/refgame2.0/graphical_conventions_group_data_run5_submitButton_diagnosticity.csv')) %>%
  select(-png, -svgString) %>%
  filter(!is.na(diagnosticity))

d.objectmap <- read_csv(here('data/diagnosticity/refgame2.0/semantic_mapping_annotations_object.csv'))
d.strokemap <- read_csv(here('data/diagnosticity/refgame2.0/semantic_mapping_annotations_stroke.csv')) 
```

```{r}
d.objectmap  %>% pull(aID) %>% unique() %>% length()
d.strokemap  %>% pull(annotatorID) %>% unique() %>% length()
d.strokemap  %>% unite(id, gameID, targetID, repetition) %>% pull(id) %>% unique() %>% length()
```

```{r}
# we checked that these don't affect the outcome
outliers <- c('5535-af4e7c1c-b29d-4130-b236-7c050622d17e', '9345-78852c80-4277-4c8a-b950-7fec3d6b6c29')
library(lmerTest)
d.diagnosticity %>%
  filter(phase != "repeated") %>%
  mutate(phase = factor(phase), condition = factor(condition)) %>%
  lmer(scale(diagnosticity) ~ phase * condition + (1 + phase + condition | target) + (1 +  condition | gameID),
       data = .,
       contrasts = list(phase = contr.sum(2), condition = contr.sum(2))) %>%
  summary()
```

## Plot changes in overall diagnosticity (Fig. 7)

```{r}
d.diagnosticity %>%
  filter(phase %in% c('pre', 'post')) %>%
  mutate(phase = fct_relevel(phase, 'pre', 'repeated')) %>%
  group_by(phase, condition) %>%
  tidyboot::tidyboot_mean(diagnosticity) %>%
  ggplot(aes(x = phase, y = empirical_stat, color = condition, group = condition)) +
    geom_line(size = 1.5, position=position_dodge(.05)) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0, size = 1.5, position = position_dodge(.05)) +
    labs(y = 'mean diagnosticity', x = '') +
    ylim(0.3, 0.4) +
    scale_color_manual(values = c('#808080', '#163C4E')) +
    theme_few() +
    theme(aspect.ratio = 1)

ggsave(paste0('plots/refgame', version, '/diagnosticity_change.pdf'),
       width = 4, height = 4)
```

```{r}
d.diagnosticity %>%
  filter(phase %in% c('pre', 'post')) %>%
  select(gameID, target, condition, phase, diagnosticity) %>%
  spread(phase, diagnosticity) %>%
  mutate(diff = post - pre) %>%
  group_by(gameID, condition) %>%
  summarize(diff = mean(diff)) %>%
  spread(condition, diff) %>%
  mutate(double_diff = repeated - control) %>%
  gather(condition, diff, repeated, control) %>%
  group_by(condition) %>%
  mutate(mean_diff = mean(diff, na.rm = T)) %>%
  ggplot(aes(x = condition, y = diff)) +
    geom_line(aes(group = gameID, color = double_diff > 0), alpha = 0.5) +
    geom_point(aes(color = double_diff > 0), alpha = 0.25) +
    geom_point(aes(y = mean_diff), size = 4) +
    geom_line(aes(y = mean_diff, group = 1), size = 2, color = 'black') +
    geom_hline(yintercept = 0, linetype = 'dotted') +
    labs(y = 'mean change in diagnosticity', x = '') +
    theme_few() +
    theme(aspect.ratio = 1, legend.position = 'none')
```

# Supplemental analyses

## Relationship between intesity and diagnosticity 

If people aren't changing their sketches at all, we don't really expect diagnosticity to change.

Here we look at the relationship between intensity change and diagnosticity change, i.e. conditioned on people who actually changed the way they drew, did it make it more or less diagnostic?

```{r}
d.diagnosticity %>%
  filter(phase %in% c('pre', 'post')) %>%
  select(gameID, target, condition, phase, intensity, diagnosticity) %>%
  gather(measure, value, intensity, diagnosticity) %>%
  spread(phase, value) %>%
  mutate(diff = post - pre) %>%
  select(-post, -pre) %>%
  spread(measure, diff) %>%
  group_by(condition) %>%
  mutate(diagnosticity = scale(diagnosticity),
         intensity = scale(intensity),
         mean_diagnost = mean(diagnosticity, na.rm = T),
         mean_intensity = mean(intensity, na.rm = T)) %>%
  ggplot(aes(x = intensity, y = diagnosticity)) +
    geom_point(alpha = 0.1, size = 1) +
    geom_smooth(method = 'lm', se=T, fullrange=TRUE ) +
    xlim(-5,5) +
    ylim(-5,5) +
    geom_point(aes(x = mean_diagnost, y = mean_intensity), size = 4) +
    theme_classic() +
    theme(aspect.ratio = 1)

ggsave('diagnosticity_change.pdf')
```

```{r}
d.cor <-d.diagnosticity %>%
  filter(phase %in% c('pre', 'post')) %>%
  select(gameID, target, condition, phase, intensity, diagnosticity) %>%
  gather(measure, value, intensity, diagnosticity) %>%
  spread(phase, value) %>%
  mutate(diff = post - pre) %>%
  select(-post, -pre) %>%
  spread(measure, diff) %>%
  mutate(diagnosticity = scale(diagnosticity),
         intensity = scale(intensity),
         mean_diagnost = mean(diagnosticity, na.rm = T),
         mean_intensity = mean(intensity, na.rm = T)) %>%
  filter(intensity > -4, intensity < 4) #%>%

cor.test(d.cor$intensity, d.cor$diagnosticity, method = 'pearson', use = 'na.or.complete')
```

Alt way of running diagnosticity regression purely on difference scores?

```{r}
d.diagnosticity %>%
  filter(phase %in% c('pre', 'post')) %>%
  select(gameID, target, condition, phase, intensity, diagnosticity) %>%
  gather(measure, value, intensity, diagnosticity) %>%
  spread(phase, value) %>%
  mutate(diff = post - pre) %>%
  select(-post, -pre) %>%
  spread(measure, diff) %>%
  lmer(diagnosticity ~ condition + (1 | gameID) + (1 | target), 
       data = .,
       control = lmerControl(optimizer = 'bobyqa')) %>%
    summary()
```

## Probe source of diagnosticity change

Note that diagnosticity can go up because either (1) additional diagnostic strokes that didn't appear at the beginning were ADDED by the end or (2) undiagnostic strokes at the beginning were REMOVED by the end. 

```{r}
d.overlap <- read_csv(here('./data/diagnosticity/graphical_conventions_group_data_run5_submitButton_sketchOverlap.csv')) %>%
  group_by(obj_id) %>%
  mutate(rep1 = floor((row_number() -1) / 8),
         rep2 = (row_number() - 1) %% 8) %>%
  filter(rep1 == 0, rep2 == 7)

d.overlap %>%
  gather(measure, value, IOU, AOU, BOU) %>%
  ggplot(aes(x = measure, y = value, color = measure)) +
    geom_boxplot() +
    geom_jitter(alpha = 0.05) +
    theme_classic() +
    theme(aspect.ratio = 1)
```

```{r}
d.overlap %>%
  ggplot(aes(x = AOU, y = BOU)) +
    geom_bin2d() +
    geom_abline(intercept = 1, slope = -1) +
    geom_abline(intercept = 0, slope = 1, linetype = 'dashed', alpha = 0.25) +
    ylim(0,1) +
    xlim(0,1) +
    theme_classic() +
    theme(aspect.ratio = 1)
```


```{r}
d.overlap %>%
  group_by(rep1, rep2) %>%
  do(fit =cor.test(.$diagnosticity_change, .$AOU, method = 'spearman', use = "pairwise.complete.obs")) %>%
  tidy(fit) %>%
  mutate(p.value.coarse = case_when(is.na(p.value) ~ 'NA',
                                    p.value > 0.05 ~ 'n.s.',
                                    p.value > 0.01 ~ '*',
                                    p.value > 0.001 ~ '**',
                                    TRUE ~ '***')) %>%
  ungroup() %>%
  mutate(p.value.coarse = as.factor(p.value.coarse),
         p.value.coarse = fct_relevel(p.value.coarse, 'NA', 'n.s.', '*', '**', '***')) %>%
  ggplot(aes(x = rep1, y = rep2, fill = p.value.coarse)) +
    geom_tile() +
    theme_classic() +
    theme(aspect.ratio = 1) +
    scale_y_reverse() +
    scale_fill_brewer(palette = 'Blues')
```

Look at response latency of annotators?

```{r}
d_stroke_annotations <- read_csv('../results/csv/semantic_mapping_annotations_stroke.csv')
d_stroke_annotations %>% 
  mutate(logLatency = log(responseLatency)) %>%
  ggplot(aes(x = logLatency))  +
    geom_histogram(bins = 50) +
    geom_vline(xintercept = 8) +
    theme_classic()
```

## Histograms for bis, numCurvesPerSketch and numStrokes 

```{r}
d.bis.drawDuration %>% 
  ggplot(aes(x = bis)) +
    geom_histogram(bins=50)
```

```{r}
d %>% 
  group_by(numCurvesPerSketch) %>% 
  ggplot(aes(x = numCurvesPerSketch)) +
    geom_histogram()
```

```{r}
d %>% 
  group_by(numStrokes) %>% 
  ggplot(aes(x = numStrokes)) + 
    geom_histogram()
```

## Within-interaction drift

```{r}
true_lmer.drift <- make_within_df(M_mat, F_mat_raw_nonorm, 'cor') %>% 
  filter(rep1 == 0) %>% 
  ungroup()
true_lmer.drift.out <- lmer(sim ~ poly(rep2,2) + (1  | gameID) + (1 | target), data = true_lmer.drift)

# scramble repetition
permuted_tstats.drift <- map_dbl(seq_len(1000), ~ M_mat %>%
  group_by(target, repetition) %>% mutate(gameID = sample(gameID)) %>% ungroup() %>%
  arrange(gameID, target, repetition) %>%
  make_within_df(F_mat_raw_nonorm, 'cor') %>%
  filter(rep1 == 0) %>% 
  ungroup() %>%  mutate(sample_id = 1) %>% split(.$sample_id) %>%
  map(~ lmer(sim ~ poly(rep2,2) + (1 | gameID) + (1 | target), data = .)) %>%
  map(~ (tidy(., effects = 'fixed') %>% filter(term == 'poly(rep2, 2)1'))$statistic) %>%
  unlist())

cat('CI for drift analysis=', sort(permuted_tstats.drift)[25], sort(permuted_tstats.drift)[975])
cat('true for drift analysis=', (tidy(true_lmer.drift.out, effects = 'fixed') %>% filter(term == 'poly(rep2, 2)1'))$statistic)
```

Plot change in similarity between successive drawings of same object (by same sketcher) against permuted baseline measuring the similarity between drawings of the same object across successive repetitions, but produced by different sketchers ("drift") 

```{r}
num_permutations <- 1000
empirical.drift <- compute_within_drift(M_mat, F_mat_raw_nonorm, 'empirical', method = 'cor', nboot = 1000)
baselines.drift <- map_dfr(seq_len(num_permutations), ~M_mat %>%
  group_by(target, repetition) %>%
  mutate(gameID = sample(gameID)) %>% # shuffle within target-rep 
  ungroup() %>%
  arrange(gameID, target, repetition) %>%
  compute_within_drift(F_mat_raw_nonorm, .x, method = 'cor')) # this passes in the iteration number
```

```{r}
d.toplot.drift <- baselines.drift %>%
  group_by(`rep diff`) %>%
  summarize(`ci_upper`=quantile(empirical_stat, probs=0.975),
            `ci_lower`=quantile(empirical_stat, probs=0.025),
            `empirical_stat`=quantile(empirical_stat, probs=0.5)) %>%
  mutate(sample_id = 'baseline') %>%
  rbind(empirical.drift %>% select(-n, -mean)) 

ggplot(d.toplot.drift, aes(x = `rep diff`, y = empirical_stat, 
             fill = sample_id, color = sample_id, group = sample_id)) +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.5, color = NA,
                d.toplot.drift %>% filter(sample_id == 'baseline')) +
    geom_line(size = 1, linetype = 'dashed', data = d.toplot.drift %>% filter(sample_id == 'baseline')) +
    geom_point(size = 2, data = d.toplot.drift %>% filter(sample_id == 'empirical')) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0,
                  data = d.toplot.drift %>% filter(sample_id == 'empirical')) +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F,
                data = d.toplot.drift %>% filter(sample_id == 'empirical')) +
    scale_color_manual(values=c("#d07e93", "#163c4e")) + 
    scale_fill_manual(values=c("#d07e93", "#163c4e")) + 
    scale_x_discrete(labels = c('(1,2)','(1,3)', '(1,4)', '(1,5)', '(1,6)' ,'(1,7)','(1,8)')) +
    ylim(.5, .8) +
    ylab('correlation') +
    ggtitle('drift from initial') +
    theme_few() +
    xlab('repetition pair') +
    guides(color = F, fill = F) +
    theme(legend.position = c(0.5, 0.8), text = element_text(size=18), 
          element_line(size=1), element_rect(size=2, color="#00000"))

ggsave(paste0('plots/refgame', version, '/drift.pdf'), height = 10, width = 7, units = 'cm', useDingbats = F)
```

Perform variant of the above analysis, except substitute in a different permuted baseline where drawings are from the same sketcher, but of different objects across successive repetitions

```{r}
num_permutations <- 1000
empirical.drift <- compute_within_drift(M_mat, F_mat_raw_nonorm, 'empirical', method = 'cor', nboot = 1000)
baselines.drift.sameSketcher <- map_dfr(seq_len(num_permutations), ~M_mat %>%
  group_by(gameID, repetition) %>%
  mutate(gameID = sample(target)) %>% # shuffle targets within gameID-repetition
  ungroup() %>%
  arrange(gameID, target, repetition) %>%
  compute_within_drift(F_mat_raw_nonorm, .x, method = 'cor')) # this passes in the iteration number
```

```{r}
d.toplot.drift <- baselines.drift.sameSketcher %>%
  group_by(`rep diff`) %>%
  summarize(`ci_upper`=quantile(empirical_stat, probs=0.975),
            `ci_lower`=quantile(empirical_stat, probs=0.025),
            `empirical_stat`=quantile(empirical_stat, probs=0.5)) %>%
  mutate(sample_id = 'baseline') %>%
  rbind(empirical.drift %>% select(-n, -mean)) 

ggplot(d.toplot.drift, aes(x = `rep diff`, y = empirical_stat, 
             fill = sample_id, color = sample_id, group = sample_id)) +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.5, color = NA,
                d.toplot.drift %>% filter(sample_id == 'baseline')) +
    geom_line(size = 1, linetype = 'dashed', data = d.toplot.drift %>% filter(sample_id == 'baseline')) +
    geom_point(size = 2, data = d.toplot.drift %>% filter(sample_id == 'empirical')) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0,
                  data = d.toplot.drift %>% filter(sample_id == 'empirical')) +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F,
                data = d.toplot.drift %>% filter(sample_id == 'empirical')) +
    scale_color_manual(values=c("#d07e93", "#163c4e")) + 
    scale_fill_manual(values=c("#d07e93", "#163c4e")) + 
    scale_x_discrete(labels = c('(1,2)','(1,3)', '(1,4)', '(1,5)', '(1,6)' ,'(1,7)','(1,8)')) +
    ylim(.5, .8) +
    ylab('correlation') +
    ggtitle('drift from initial') +
    theme_few() +
    xlab('repetition pair') +
    guides(color = F, fill = F) +
    theme(legend.position = c(0.5, 0.8), text = element_text(size=18), 
          element_line(size=1), element_rect(size=2, color="#00000"))
```


## Visualize effects of different pre-processing steps and distance metrics

```{r}
F_mat_raw_norm = as.matrix(read_delim('../../data/sketch_features/no_crop/FEATURES_FC6_sketch_channel-norm.txt',
                                   delim=',', col_names=F))
F_mat_PCA_nonorm = as.matrix(read_delim('../../data/sketch_features/no_crop/FEATURES_FC6_sketch_PCA_512_no-channel-norm.txt',
                                   delim=',', col_names=F))
F_mat_PCA_norm = as.matrix(read_delim('../../data/sketch_features/no_crop/FEATURES_FC6_sketch_PCA_512_channel-norm.txt',
                                   delim=',', col_names=F))

colnames(F_mat_raw_norm) <- NULL
colnames(F_mat_PCA_nonorm) <- NULL
colnames(F_mat_PCA_norm) <- NULL
rbind(compute_across_similarity(filtered_M, F_mat_raw_nonorm, 'raw_euclid_nonorm', method = 'euclidean'),
      compute_across_similarity(filtered_M, F_mat_raw_norm,   'raw_euclid_norm',   method = 'euclidean'),
      compute_across_similarity(filtered_M, F_mat_PCA_nonorm, 'PCA_euclid_nonorm', method = 'euclidean'),
      compute_across_similarity(filtered_M, F_mat_PCA_norm,   'PCA_euclid_norm',   method = 'euclidean'),
      compute_across_similarity(filtered_M, F_mat_raw_nonorm, 'raw_cor_nonorm',    method = 'cor'),
      compute_across_similarity(filtered_M, F_mat_raw_norm,   'raw_cor_norm',      method = 'cor'),
      compute_across_similarity(filtered_M, F_mat_PCA_nonorm, 'PCA_cor_nonorm',    method = 'cor'),
      compute_across_similarity(filtered_M, F_mat_PCA_norm,   'PCA_cor_norm',      method = 'cor')) %>%
      separate(sample_id, into = c('PCA', 'dist', 'norm')) %>%
      ggplot(aes(x = repetition, y = empirical_stat, color = norm)) + 
        geom_line() +
        geom_ribbon(aes(ymax = ci_upper, ymin = ci_lower), color = NA, alpha = .5) +
        theme_few() +
        facet_grid(dist ~ PCA, scales = 'free') +
        theme(aspect.ratio = 2)
#ggsave('unfiltered.pdf')
```

How well are these different steps correlated?

```{r}
rbind(compute_across_similarity(M_mat, F_mat_PCA_norm, 'PCA_cor_norm',    method = 'cor'),
      compute_across_similarity(M_mat, F_mat_raw_nonorm, 'raw_cor_nonorm',    method = 'cor')) %>%
  select(repetition, sample_id, empirical_stat) %>%
  spread(sample_id, empirical_stat) %>%
  mutate(spcor = cor(PCA_cor_norm,raw_cor_nonorm, method='pearson')) %>%
  ggplot(aes(x = PCA_cor_norm, y = raw_cor_nonorm)) +
      geom_point() +
      geom_smooth() +
      theme_few()
```

Broken out by target

```{r}
M_mat %>%
  group_by(target, repetition) %>%
  do(flatten_sim_matrix(get_sim_matrix(., F_mat_raw_nonorm, method = 'cor'),
                        .$gameID)) %>%
  unite(col = 'gamepair', dim1, dim2) %>%
  ggplot(aes(x = repetition, y = sim, group = gamepair)) +
    geom_line(alpha = .1) +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), group = 1) +
    facet_wrap(~ target) +
    theme_few()
```
